Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

@@

\section{Methods}
We ran the system with several hundred different combinations of features over
all the words in the input set.

@@

We ran a more detailed analysis on the top system.  This analysis included
consideration of all three grain-levels of score and scores by word.

>>>>

\subsection{Selecting optimal feature combination}
\newcommand\ward{backward} %or maybe backwards

We used a \ward stepwise approach to identifying optimal feature combinations.
We first ran the system with all features on, producing a total of $256=2^8$
combinations.  We then used backwards stepwise regression to identify feature
combinations with a small number of features but with high performance

@@

\section{Methods}
\newcommand\few{few}

We ran the system with several hundred different combinations of features over
all the words in the input set.

@@

We ran a more detailed analysis on the top \few systems.  This analysis included
consideration of all three grain-levels of score and scores by word.
